TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-14 paper/draft.tex
to-do comments

JB REDO 3 CMD PLOTS SHOWING BEFORE AND AFTER SELECTION.

@@

%---------------------------
\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/demo_derivatives_teff1.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff2.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff3.png}
\end{center}
\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallcities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463$K; error estimate computed using a jackknife statistic at each pixel is marked in red, making it possible to distinguish which features vary significantly with change in spectral type, and which are likely due to noise.}\label{fig:demo_teff}
\end{figure}

>>>>

@@

%---------------------------
\begin{figure}[ht]
\begin{center}
\includegraphics[width=16cm]{figures/demo_derivatives_teff1.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff2.png}
\includegraphics[width=16cm]{figures/demo_derivatives_teff3.png}
\end{center}
\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallcities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463$K; error estimate computed using a jackknife statistic at each pixel is marked in red, making it possible to distinguish which features vary significantly with change in spectral type, and which are likely due to noise. JB: ADD CHI^2 FIT TO PLOT}\label{fig:demo_teff}
\end{figure}
